---
title: "NASA API Package Vignette"
author: "Haoxiang Xu, Zetian Zhao, Litao Zheng"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# NASA API Wrapper

## Introduction

This vignette demonstrates how to use the "nasaR" package — a wrapper for several NASA RESTful APIs. The package provides eight functions listed below:

-   **get_apod_photo()** – Fetch NASA’s Astronomy Picture of the Day with descriptions.

-   **get_earth_image()** – Download NASA satellite imagery by geographic coordinates.

-   **get_earth_landsat_imagery()** – Retrieve Landsat satellite images of Earth.

-   **get_earth_polychromatic_imaging()** – Access DSCOVR EPIC images of Earth in multiple wavelengths.

-   **get_mars_rover_photos()** – Retrieve images captured by NASA’s Mars rovers.

-   **get_mars_weather()** – Get the latest weather reports from NASA’s Mars missions.

-   **get_neo_data()** – Access Near-Earth Object details and visualize asteroid data.

-   **search_nasa_images()** – Search for NASA images and videos using keywords.

## Installation

Package Installation

```{r}
install.packages("nasaR/nasaR_0.0.0.9000.tar.gz", repos = NULL, type ="source", quiet = TRUE)
```

Import Library

```{r}
library(nasaR)
```

Import Other Libraries

```{r}
library(png)
```

## Functions Detail

### **get_apod_photo()**

Fetch NASA’s Astronomy Picture of the Day with descriptions.

**Required parameters**

| Parameter    | Description              | Default |
|--------------|--------------------------|---------|
| `api_key`    | NASA API key             | NULL    |
| `show_image` | Display the image or not | TRUE    |

```{r}
# Example
# api_key <- <<<ENTER API KEY HERE>>>
# get_apod_photo(api_key, show_image = FALSE)
```

#### Example output

```{r}
img <- readPNG("sample_output/get_apod_photo_output.png")
par(mar = c(0, 0, 0, 0))
plot(NA, type = "n", xlim = c(0, 1), ylim = c(0, 1), axes = FALSE, xlab = "", ylab = "")
rasterImage(img, 0, 0, 1, 1)
```


### **get_earth_image()**

Download NASA satellite imagery by geographic coordinates.

| Parameter | Description             | Default    |
|-----------|-------------------------|------------|
| `api_key` | NASA API key            | NULL       |
| `lat`     | Latitude (-90 to 90)    | NULL       |
| `lon`     | Longitude (-180 to 180) | NULL       |
| `date`    | Date (YYYY-MM-DD)       | Sys.Date() |
| `dim`     | Image size in degrees   | 0.1        |

```{r}
# Example
# api_key <- <<<ENTER API KEY HERE>>>
lat <- 37.7749
lon <- -122.4194
# get_earth_image(api_key, lat, lon)
```

#### Example output

```{r}
img <- readPNG("sample_output/get_earth_image_output.png")
par(mar = c(0, 0, 0, 0))
plot(NA, type = "n", xlim = c(0, 1), ylim = c(0, 1), axes = FALSE, xlab = "", ylab = "")
rasterImage(img, 0, 0, 1, 1)
```


### **get_earth_landsat_imagery()**

Retrieve Landsat satellite images of Earth.

| Parameter        | Description             | Default    |
|------------------|-------------------------|------------|
| `api_key`        | NASA API key            | NULL       |
| `lat`            | Latitude (-90 to 90)    | NULL       |
| `lon`            | Longitude (-180 to 180) | NULL       |
| `dim`            | Image size in degrees   | 0.025      |
| `date`           | Date (YYYY-MM-DD)       | Sys.Date() |
| `cloud_score`    | Cloud score             | FALSE      |
| `download_image` | Save image or not       | FALSE      |

```{r}
# Example
# api_key <- <<<ENTER API KEY HERE>>>
lat <- 40.7128
lon <- -74.0060
# get_earth_landsat_imagery(api_key, lat, lon, download_image = TRUE)
```

#### Example output

```{r}
img <- readPNG("sample_output/get_earth_landsat_imagery_output.png")
par(mar = c(0, 0, 0, 0))
plot(NA, type = "n", xlim = c(0, 1), ylim = c(0, 1), axes = FALSE, xlab = "", ylab = "")
rasterImage(img, 0, 0, 1, 1)
```


### **get_earth_polychromatic_imaging()**

Access DSCOVR EPIC images of Earth in multiple wavelengths.

| Parameter        | Description       | Default    |
|------------------|-------------------|------------|
| `api_key`        | NASA API key      | NULL       |
| `endpoint`       | EPIC endpoint     | natural    |
| `date`           | Date (YYYY-MM-DD) | Sys.Date() |
| `download_image` | Save image or not | FALSE      |

```{r}
# Example
# api_key <- <<<ENTER API KEY HERE>>>
# get_earth_polychromatic_imaging(
#   api_key = api_key,
#   endpoint = "natural/date",
#   date = "2019-05-30",
#   download_image = TRUE
# )
```

#### Example output

```{r}
img <- readPNG("sample_output/get_earth_polychromatic_imaging_output.png")
par(mar = c(0, 0, 0, 0))
plot(NA, type = "n", xlim = c(0, 1), ylim = c(0, 1), axes = FALSE, xlab = "", ylab = "")
rasterImage(img, 0, 0, 1, 1)
```


### **get_mars_rover_photos()**

Retrieve images captured by NASA’s Mars rovers.

| Parameter    | Description                   | Default |
|--------------|-------------------------------|---------|
| `api_key`    | NASA API key                  | NULL    |
| `sol`        | Integer for Martian sol (day) | NULL    |
| `earth_date` | Date (YYYY-MM-DD)             | NULL    |

```{r}
# Example
# api_key <- <<<ENTER API KEY HERE>>>
# get_mars_rover_photos(api_key, sol = 1000)
```

#### Example output

```{r}
img <- readPNG("sample_output/get_mars_rover_photos_output.png")
par(mar = c(0, 0, 0, 0))
plot(NA, type = "n", xlim = c(0, 1), ylim = c(0, 1), axes = FALSE, xlab = "", ylab = "")
rasterImage(img, 0, 0, 1, 1)
```


### **get_mars_weather()**

Get the latest weather reports from NASA’s Mars missions.

| Parameter | Description        | Default |
|-----------|--------------------|---------|
| `api_key` | NASA API key       | NULL    |
| `version` | API version number | 1.0     |

```{r}
# Example
# api_key <- <<<ENTER API KEY HERE>>>
# get_mars_weather(api_key, version = 1.0)
```

#### Example output

```{r}
img <- readPNG("sample_output/get_mars_weather_output.png")
par(mar = c(0, 0, 0, 0))
plot(NA, type = "n", xlim = c(0, 1), ylim = c(0, 1), axes = FALSE, xlab = "", ylab = "")
rasterImage(img, 0, 0, 1, 1)
```


### **get_neo_data()**

Access Near-Earth Object details and visualize asteroid data.

| Parameter    | Description  | Default |
|--------------|--------------|---------|
| `api_key`    | NASA API key | NULL    |
| `start_date` | Start date   | NULL    |
| `END_date`   | End date     | NULL    |

```{r}
# Example
# api_key <- <<<ENTER API KEY HERE>>>
# get_neo_data(
#   api_key, 
#   start_date = "2023-01-01", 
#   end_date = "2023-01-02")
```

#### Example output

```{r}
img <- readPNG("sample_output/get_neo_data_output.png")
par(mar = c(0, 0, 0, 0))
plot(NA, type = "n", xlim = c(0, 1), ylim = c(0, 1), axes = FALSE, xlab = "", ylab = "")
rasterImage(img, 0, 0, 1, 1)
```


### **search_nasa_images()**

Search for NASA images and videos using keywords.

| Parameter | Description                    | Default |
|-----------|--------------------------------|---------|
| `query`   | Character string to search for | NULL    |

```{r}
# Example
# search_nasa_images(query = "mars")
```

#### Example output

```{r}
img <- readPNG("sample_output/search_nasa_images_output.png")
par(mar = c(0, 0, 0, 0))
plot(NA, type = "n", xlim = c(0, 1), ylim = c(0, 1), axes = FALSE, xlab = "", ylab = "")
rasterImage(img, 0, 0, 1, 1)
```

